\showyourwork: a workflow for open source scientific articles

### 2022-09-22 src/tex/ms.tex
cuter

\xxx{Discuss Table~\ref{tab:variable} and variable output.}
Variable output can also occur inline. For instance, the following sentence is programmatically generated from the same script: \variable{output/SHO_value.tex} Note the icon in the margin that automatically links to the corresponding \snakemake rule.

>>>>

\xxx{Discuss Table~\ref{tab:variable} and variable output.}
Variable output can also occur inline. For instance, the following sentence is programmatically generated from the same script: 
\variable{output/kernel_value.tex} 
Note the icon in the margin that automatically links to the corresponding \snakemake rule, where users can easily change the values of the kernel parameters.
